Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-15 WSSSPE2_report/WSSSPE2_review.tex
Section 4: touch up.
adding intro to software dev section from Nancy

\item \textbf{John Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub}

%Affiliation: Idaho National Laboratory

Peterson from the the Idaho National Laboratory reported that in March 2014, the MOOSE framework was released under an open
source license on GitHub, significantly expanding and diversifying the pool of
current active and potential future contributors on the project. The MOOSE team
employs an extensive continuous integration test suite to ensure that both the
framework and the applications based on the framework are verified before any
code changes are accepted into the repository. They use a combination of built-in
git features such as branching and submodules, GitHub API integration
capabilities, and in-house developed testing software to perform this
verification and update the dependent applications in a relatively seamless
manner for users.

@@

\katznote{need some short general intro to Software Development Experiences here}

@@

Because of the large number of submitted papers categorized as Software
Development Experiences, papers were split into two subgroups prior to the
workshop.

\katznote{need something about subgroup A too}

>>>>

\item \textbf{John Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub} 
%Affiliation: Idaho National Laboratory
Peterson from the the Idaho National Laboratory reported that in March 2014, the MOOSE framework was released under an open
source license on GitHub, significantly expanding and diversifying the pool of
current active and potential future contributors on the project. The MOOSE team
employs an extensive continuous integration test suite to ensure that both the
framework and the applications based on the framework are verified before any
code changes are accepted into the repository. They use a combination of built-in
git features such as branching and submodules, GitHub API integration
capabilities, and in-house developed testing software to perform this
verification and update the dependent applications in a relatively seamless
manner for users.

@@

Of the short actionable papers that would lead to improvements for sustainable
software science, 11 submissions were categorized in the  Software Development Experiences
group. Because of the large number, we split these into two subgroups
prior to the event. Some common themes helped in this division, for
example several papers that addressed education and training issues,
including best practices and case studies, were grouped
together. Others discussed experiences with registries, developer
collectives and specific examples of successful, sustainable software
(including a valuable industry perspective).

@@

\katznote{need something about subgroup A here}
